Probabilistic Catalogs for Crowded Stellar Fields

### 2013-04-08 paper/ms.tex
New version of CLF figure
Don't use the word hyperparameters

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=\textwidth]{Figures/inference1.eps}
\end{center}
\caption{Inference about the parameters for Test Case 1. The left panel shows
the posterior distribution for the number of stars $N$, and the right
panels show the joint posterior distributions for the flux distribution
(hyper)parameters. Note that there is
considerable uncertainty (particularly about $h_2$), which occurs because the
shape of the broken power-law does not depend strongly on the parameters.
The true input values are plotted as filled squares.
\label{fig:results1}}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=\textwidth]{Figures/inference2.eps}
\end{center}
\caption{Inference about the parameters for Test Case 2. Note that the
flux distribution (hyper)parameters are still not very well constrained even with
the larger number of
stars. This occurs because the fluxes of faint stars are not accurately measured
and because the shape of the broken power-law distribution does not vary rapidly
as a function of its parameters. The true input values are plotted as filled squares.\label{fig:results2}}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=\textwidth]{Figures/luminosity_function.eps}
\end{center}
\caption{The cumulative luminosity functions (number of stars above a given
flux, as a function of flux) produced by the Bayesian method
(several posterior samples shown)
and
\sex~(for various values of the threshold parameters), compared with the
actual cumulative LF. Both methods correctly identify the fluxes at the bright
end, with some uncertainty due to overlapping sources. However, at the lower
end \sex~is unable to detect all of the stars whereas the true CLF is typical
of the posterior distribution.
\label{fig:luminosity_function}}
\end{figure}

>>>>

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=\textwidth]{Figures/inference1.eps}
\end{center}
\caption{Inference about the parameters for Test Case 1. The left panel shows
the posterior distribution for the number of stars $N$, and the right
panels show the joint posterior distributions for the flux distribution
parameters. Note that there is
considerable uncertainty (particularly about $h_2$), which occurs because the
shape of the broken power-law does not depend strongly on the parameters.
The true input values are plotted as filled squares.
\label{fig:results1}}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=\textwidth]{Figures/inference2.eps}
\end{center}
\caption{Inference about the parameters for Test Case 2. Note that the
flux distribution parameters are still not very well constrained even with
the larger number of
stars. This occurs because the fluxes of faint stars are not accurately measured
and because the shape of the broken power-law distribution does not vary rapidly
as a function of its parameters. The true input values are plotted as filled squares.\label{fig:results2}}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
\includegraphics[scale=0.5]{Figures/luminosity_function.eps}
\end{center}
\caption{The cumulative luminosity functions (number of stars above a given
flux, as a function of flux) produced by the Bayesian method
(several posterior samples shown)
and
\sex~(for various values of the threshold parameters), compared with the
actual cumulative LF. Both methods correctly identify the fluxes at the bright
end, with some uncertainty due to overlapping sources. However, at the lower
end \sex~is unable to detect all of the stars whereas the true CLF is typical
of the posterior distribution.
\label{fig:luminosity_function}}
\end{figure}
